Toward Centrally Programming Distributed Control Planes

### 2016-01-24 paper/background.tex

All routing announcements are accompanied by an AS-path attribute that reflects the sequence of ASes that the announcement has traversed thus far. While the AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.  One such attribute is a list of community strings. ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast") and then use the color later in the routing process.  Communities are also used to signal to neighbors how they should handle an announcement (e.g., do not export it further). Another non-global attribute is the multi-exit discriminator (MED). It is used when an AS has more than one router-level link to a neighboring AS.  Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.

@@

>>>>

All routing announcements are accompanied by an AS-path attribute that reflects the sequence of ASes that the announcement has traversed thus far. While the AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.  One such attribute is a list of community strings. ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast") and then use the color later in the routing process.  Communities are also used to signal to neighbors how they should handle an announcement (e.g., do not export it further). Another non-global attribute is the multi-exit discriminator (MED). It is used when an AS has multiple links to a neighboring AS.  Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.

@@

In implementing their policy, each network assumes that neighboring ASes correctly implement BGP and honor contracts related to MEDs and communities. While deriving configurations, \sysname makes a similar assumption.
